\vspace{-2.0cm} \textbf{Talking with signs} \\ \Large \textbf{A method for progressively detect signs in a non annotated signs language corpus}

### 2019-11-22 article/article-tesis.tex
updates on the paper and initial work for learning models

\title{%
	\vspace{-2.0cm}
	\textbf{Talking with signs} \\	
	\Large \textbf{A method for progressively detect sings in a non annotated Peruvian Sings Language corpus}
}

@@

\begin{abstract}
People with deafness or hearing disabilities who aim to use computer based systems relies on state of art video classification and human action recognition techniques that combine traditional movement pattern recognition and deep learning techniques. In this work we present a pipeline for semi automatic video annotation applied to a non annotated \textit{Peruvian Signs Language} (PSL) corpus along with a novel method for a progressive detection of PSL elements (nSDm). We produced a set of video annotations indicating signs appearances for a small set of nouns and numbers along with a \textit{labeled PSL dataset} (PSL dataset). A composite model obtained from the combination of a 2D CNN trained with movement patterns extracted from the PSL dataset using Lucas Kanade optical flow, and a RNN with LSTM cells trained with raw rgb frames extracted from the PSL dataset achieved XX precision and XX exhaustivity on sings classification, reporting state of art results over the PSL dataset. \\
\keywords{Video Classification, Human Actions Detection, Peruvian Signs Language, Optical Flow, 2D CNN, LSTM.}
\end{abstract}

@@

As of today, thanks to Deep Learning techniques for Computer Vision and Natural Language Processing, it is completely feasible to propose and design systems that are able to detect and transcribe sign languages elements improving in systems accessibility for people with physical limitations. Sings detection is usually a supervised learning task that requires a large and fully labeled dataset in order to achieve satisfactory results during model training and inference tasks. At the time  of writing this work there were no labeled data sets available for the PSL \cite{lsp_2015}, previous work was done by the \textit{Grammar and Signs research group of the Pontifical Catholic University of Peru (PUCP)} who created the first PSL corpus \cite{lsp_dataset}, this corpus is not annotated because there is no available metadata that describes signs being emitted and

>>>>

\title{%
	\vspace{-2.0cm}
	\textbf{Talking with signs} \\	
	\Large \textbf{A method for progressively detect signs in a non annotated signs language corpus}
}

@@

\begin{abstract}
People with deafness or hearing disabilities who aim to use computer based systems relies on state of art video classification and human action recognition techniques that combine traditional movement pattern recognition and deep learning techniques. In this work we present a pipeline for semi automatic video annotation applied to a non annotated \textit{Peruvian Signs Language} (PSL) corpus along with a novel method for a progressive detection of PSL elements (nSDm). We produced a set of video annotations indicating signs appearances for a small set of nouns and numbers along with a \textit{labeled PSL dataset} (PSL dataset). A composite model obtained from the combination of a 2D CNN trained with movement patterns extracted from the PSL dataset using Lucas Kanade optical flow, and a RNN with LSTM cells trained with raw rgb frames extracted from the PSL dataset achieved XX precision and XX exhaustivity on sings classification tasks, reporting state of art results over the PSL dataset. \\
\keywords{Video Classification, Human Actions Detection, Peruvian Signs Language, Optical Flow, 2D CNN, LSTM.}
\end{abstract}

@@

With today's Deep Learning techniques for Computer Vision and Natural Language Processing it is completely feasible to propose and design systems that are able to detect and transcribe sign languages elements improving in systems accessibility for people with physical limitations. Sings detection is usually a supervised learning task that requires a large and fully labeled dataset in order to achieve satisfactory results during model training and inference tasks. At the time  of writing this work there were no labeled data sets available for the PSL \cite{lsp_2015}, previous work was done by the \textit{Grammar and Signs research group of the Pontifical Catholic University of Peru (PUCP)} who created the first PSL corpus \cite{lsp_dataset}, this corpus is not annotated because there is no available metadata that describes signs being emitted and
